Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-02 soc_squeezing/cumulant_expansions.tex
added text about avoiding null terms in the product of multi-body opeators

      \abs{\set{j_\alpha^\mu}\cap\set{k_\beta^\nu}}=s}} X,

@@

where the sum over $s$ terminates after $s = \sum_\mu\p{m_\mu+n_\mu}$.

@@

>>>>

      \abs{\set{j_\alpha^\mu}\cap\set{k_\beta^\nu}}=s}} X.

@@

@@

The sums in \eqref{eq:SS_simp} generally involve a large number of
terms; in practice, many of these terms will be equal to zero.  We
can, however, impose additional restrictions on these sums in such a
way as to throw out terms which vanish, and keep those which do not.
Remembering that $s$ counts the number of spins which are addressed by
both operators $P_{\v j}$ and $P_{\v k}$ in \eqref{eq:SS_PP}, the
first restriction we can impose comes from recognizing that for given
$\S_{\v m},\S_{\v n}$, the overlap $s$ is bounded as
\begin{align}
  \max\set{0,\sum_\mu\p{m_\mu+n_\mu}-N}
  \le s \le \min\set{N,\sum_\mu\p{m_\mu+n_\mu}}.
\end{align}
In addition, the group multiplication table $\eta_{\mu\nu\kappa}$ may
generally contain zeros that we can preemptively avoid with
restrictions on $\v r$ and $\v\rho$.  Recalling that $r_{\mu\nu}$
counts the number of operators addressed by
$\sigma_\mu\sigma_\nu=\sum_\kappa\eta_{\mu\nu\kappa}\sigma_\kappa$, if
$\eta_{\mu\nu\kappa}=0$ for all $\kappa$,
i.e.~$\sigma_\mu\sigma_\nu=0$, then any term with $r_{\mu\nu}>0$ will
vanish.  Our second restriction on the sums in \eqref{eq:SS_simp} is
therefore to fix $r_{\mu\nu}=r_{\nu\mu}=0$ for all $\mu,\nu$ for which
$\sigma_\mu\sigma_\nu=0$.  Finally, we can avoid the nullifying effect
of any additional zeros in the multiplication table
$\eta_{\mu\nu\kappa}$ by restricting $\rho^{\mu\nu}_\kappa=0$ for all
$\mu,\nu,\kappa$ for which $\eta_{\mu\nu\kappa}=0$.  These
restrictions are sufficient to ensure that all individual terms in
\eqref{eq:SS_simp} are nonzero, although they do not rule out the
possibility of several terms canceling out.
